Metrics

### 2023-11-19 src/metrics.Rmd
Finish pccc and csmf calcs

# Name formatting vars
models_format <- c(
    "_cghr10" = "",
    "_" = " & ",
    "chatgpt3" = "ChatGPT-3",
    "chatgpt4" = "ChatGPT-4",
    "insilicova" = "InSilicoVA",
    "interva5" = "InterVA-5"
)
```

@@

    # Format display and return
    out <- out %>%
        mutate(Model = str_replace_all(Model, models_format)) %>%
        arrange(across({{name}}, desc))
    return(out)
}
```

@@

Calculate Partial Chance Corrected Concordance (PCCC) to evaluate indivudal performance for each model.

```{r}
pccc <- list()

# Calc overall pccc
pccc$all <- calc_per_model(
    actual = df %>% pull(physician_cghr10),
    pred = df %>% select(ends_with("_cghr10"), -physician_cghr10),
    func = calc_pccc
) %>% rename(
    PCCC = Metric
)

    # Filter data for age
    df_age <- df %>% filter(age == age_group)
    metric_name = paste0("PCCC ", str_to_title(age_group))

    # Calc metric for age
    pccc[[age_group]] <- calc_per_model(
        actual = df_age %>%
            pull(physician_cghr10),
        pred = df_age %>%
            select(ends_with("_cghr10"), -physician_cghr10),
        func = calc_pccc
    ) %>% rename(
         {{ metric_name }} := Metric
    )
}

# Combine all pccc metrics
pccc <- reduce(
    pccc,
    function(x, y) left_join(x, y, by = "Model")
) %>%
    arrange(desc(PCCC))
pccc
```

@@

Calculate Cause Specific Mortality Fraction (CSMF) Accuracy to evaluate population performance for each model.

```{r}
csmf_acc <- list()
```

#### Overall CSMF Accuracy

```{r}
csmf_acc <- calc_per_model(
    physicians,
    models,
    calc_csmf_acc,
    "CSMF Accuracy"
)
csmf_acc
```

#### Adult Accuracy

#### Child Accuracy

#### Neonate Accuracy

>>>>

```{r}
models_format <- c(
    "_cghr10" = "",
    "_" = " & ",
    "chatgpt3" = "ChatGPT-3",
    "chatgpt4" = "ChatGPT-4",
    "insilicova" = "InSilicoVA",
    "interva5" = "InterVA-5"
)
stage_format <- c(
    "is_" = "",
    "recon" = "Reconciliation",
    "agreed" = "Agreement",
    "adj" = "Adjudication"
)
```

@@

    # Format display and return
    out <- out %>%
        mutate(Model = str_replace_all(Model, models_format)) %>%
        arrange(across({{name}}, desc))
    return(out)
}

# Bulk calc per model based on age and physician coding stage
calc_by_age_stage <- function(df, func, name = "Metric") {
    out <- list()

    # Calc overall metric
    out[[name]] <- calc_per_model(
        actual = df %>% pull(physician_cghr10),
        pred = df %>% select(ends_with("_cghr10"), -physician_cghr10),
        func = func
    ) %>% rename(
        {{ name }} := Metric
    )

    # Calc metric for va coding stage
    for (stage in c("is_agreed", "is_recon", "is_adj")) {

        # Filter data for stage
        df_filter <- df %>% filter(.[[stage]] == TRUE)
        metric_name = paste0(
            name,
            " ",
            str_replace_all(stage, stage_format)
        )

        # Calc metric for stage
        out[[metric_name]] <- calc_per_model(
            actual = df_filter %>%
                pull(physician_cghr10),
            pred = df_filter %>%
                select(ends_with("_cghr10"), -physician_cghr10),
            func = func
        ) %>% rename(
             {{ metric_name }} := Metric
        )
    }

        # Filter data for age
        df_filter <- df %>% filter(age == age_group)
        metric_name = paste0(
            name,
            " ",
            str_to_title(age_group)
        )

        # Calc metric for age
        out[[metric_name]] <- calc_per_model(
            actual = df_filter %>%
                pull(physician_cghr10),
            pred = df_filter %>%
                select(ends_with("_cghr10"), -physician_cghr10),
            func = func
        ) %>% rename(
             {{ metric_name }} := Metric
        )

        # Calc metric for each stage within age group
        for (stage in c("is_agreed", "is_recon", "is_adj")) {

            # Filter data for stage within age group
            df_filter <- df %>% filter(
                .[[stage]] == TRUE & age == age_group
            )
            metric_name = paste0(
                name,
                " ",
                str_to_title(age_group),
                " ",
                str_replace_all(stage, stage_format)
            )

            # Calc metric for stage within age group
            out[[metric_name]] <- calc_per_model(
                actual = df_filter %>%
                    pull(physician_cghr10),
                pred = df_filter %>%
                    select(ends_with("_cghr10"), -physician_cghr10),
                func = func
            ) %>% rename(
                 {{ metric_name }} := Metric
            )
        }
    }

    # Combine all pccc metrics
    out <- reduce(out,
        function(x, y) left_join(x, y, by = "Model")
    ) %>%
        arrange(across({{ name }}, desc))
    return(out)
}
```

@@

Calculate Partial Chance Corrected Concordance (PCCC) to evaluate indivudal performance for each model by age and physician coding stage.

```{r}
pccc <- calc_by_age_stage(df, calc_pccc, "PCCC")
pccc
```

@@

Calculate Cause Specific Mortality Fraction (CSMF) Accuracy to evaluate population performance for each model by age and physician coding stage.

```{r}
csmf_acc <- calc_by_age_stage(df, calc_csmf_acc, "CSMF Accuracy")
csmf_acc
```
